FM project

### 2023-05-16 report.Rmd
updated

---
title: "FM project"
output:
  pdf_document: default
  toc: yes
  toc_depth: 2
  theme: simplex
  date: "2023-04-25"
  fig_width: 7
  fig_height: 6
  fig_caption: yes
  html_document: null
---

@@

#### Including Plots

@@

```
#### 2.3 Time Series Patterns
```{r, Seasonal plot for each product, echo=TRUE, results='markup',warning=FALSE,message=FALSE, fig.align='center', background='#F7F7F7'}
# create seasonal plot of total exports monthly of Natural gas
total_exp_oecd %>% filter(`Export type` == "Amount of Natural gas (BOE)") %>% 
  index_by(Date) %>% 
  summarise(Total_Exports = sum(`Amount`)) %>% 
  gg_season(Total_Exports) +
  ylab("Total exports  of Natural Gas") +
  ggtitle("Seasonal plot: US exports of natural gas to OECD") +
  scale_y_continuous(labels = comma_format())

@@

# create seasonal plot of total exports monthly of Petroleum products
total_exp_oecd %>% filter(`Export type` == "Amount of total Petroleum Porducts (Thousand Barrels)") %>% 
  index_by(Date) %>% 
  summarise(Total_Exports = sum(`Amount`)) %>% 
  gg_season(Total_Exports) +
  ylab("Total exports  of Petroleum Products") +
  ggtitle("Seasonal plot: US exports of Petroleum to OECD") +
  scale_y_continuous(labels = comma_format())
```
To further elaborate, the data analysis of US exports of oil products to OECD shows that seasonal patterns can differ depending on the type of product being exported. While natural gas and crude oil both display some level of seasonality, petroleum products do not show any significant trends.

@@

#Subseries plots Petroleum products
total_exp_oecd %>% filter(`Export type` == "Amount of total Petroleum Porducts (Thousand Barrels)") %>% 
  index_by(Date) %>% 
  summarise(Total_Exports = sum(`Amount`)) %>% 
  gg_subseries(Total_Exports) + 
  ylab("Total exports") + 
  ggtitle("Subseries plot: US exports of Petroleum Products")+
  scale_y_continuous(labels = comma_format())
```
To gain a better understanding of seasonality, we created additional plots known as subseries seasonal plots. These graphs provide a clearer view of monthly exports and also display the means over each month for the analyzed time series period.

@@

####2.4 ACF and White Noise

@@

### 3. Time series decomposition
#### 3.1. Adjustments

@@

#### 3.3. Decomposition

###STL Decomposition

@@

#### 4.3. Residual diagnostics

>>>>

---
title: "FM project"
output:
  pdf_document: default
  toc: yes
  toc_depth: 2
  theme: simplex
  date: "2023-04-25"
  fig_width: 7
  fig_height: 6  
  fig_caption: true
  html_document: null

---

@@

#### 2.3 Including Plots

@@

```
#### 2.4 Time Series Patterns

```{r, Seasonal plot for each product, echo=TRUE, results='markup',warning=FALSE,message=FALSE, fig.align='center', background='#F7F7F7'}
# create seasonal plot of total exports monthly of Natural gas
total_exp_oecd %>% filter(`Export type` == "Amount of Natural gas (BOE)") %>% 
  index_by(Date) %>% 
  summarise(Total_Exports = sum(`Amount`)) %>% 
  gg_season(Total_Exports) +
  ylab("Total exports  of Natural Gas") +
  ggtitle("Seasonal plot: US exports of natural gas to OECD") +
  scale_y_continuous(labels = comma_format())

@@

# create seasonal plot of total exports monthly of Petroleum products
total_exp_oecd %>% filter(`Export type` == "Amount of total Petroleum Porducts (Thousand Barrels)") %>% 
  index_by(Date) %>% 
  summarise(Total_Exports = sum(`Amount`)) %>% 
  gg_season(Total_Exports) +
  ylab("Total exports  of Petroleum Products") +
  ggtitle("Seasonal plot: US exports of Petroleum to OECD") +
  scale_y_continuous(labels = comma_format())
```

To further elaborate, the data analysis of US exports of oil products to OECD shows that seasonal patterns can differ depending on the type of product being exported. While natural gas and crude oil both display some level of seasonality, petroleum products do not show any significant trends.

@@

#Subseries plots Petroleum products
total_exp_oecd %>% filter(`Export type` == "Amount of total Petroleum Porducts (Thousand Barrels)") %>% 
  index_by(Date) %>% 
  summarise(Total_Exports = sum(`Amount`)) %>% 
  gg_subseries(Total_Exports) + 
  ylab("Total exports") + 
  ggtitle("Subseries plot: US exports of Petroleum Products")+
  scale_y_continuous(labels = comma_format())
```

To gain a better understanding of seasonality, we created additional plots known as subseries seasonal plots. These graphs provide a clearer view of monthly exports and also display the means over each month for the analyzed time series period.

@@

####2.5 ACF and White Noise

@@

### 3. Time series decomposition

#### 3.1. Adjustments

@@

#### 3.3 Decomposition

### 3.4 STL Decomposition

@@

#### 4.2. Residual diagnostics
